Overview

### 2020-10-13 overview_gh.Rmd
Update doc, add BTM Vignette
Fixing recommendation about which version to install, ref #31

---
title: "An overview of the oolong package."
output: github_document
author:
  - Chung-hong Chan ^[University of Mannheim]
---

@@

You can install the development version from [GitHub](https://github.com/) with:

@@

>>>>

---
title: "Overview"
output: github_document
author:
  - Chung-hong Chan ^[University of Mannheim]
---

@@

Because the package is constantly changing, we suggest using the development version from [GitHub](https://github.com/):

@@

You can also install the "stable" (but slightly older) version from CRAN:

```r
install.packages("oolong")
```
